Influence of Connectivity on Dung Beetle Communities

### 2025-06-17 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
update for final push

# date: "\\vspace{-1em}"
header-includes:
 # - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
 - \usepackage{lineno}
 - \linenumbers
 - \usepackage[default]{sourcesanspro}
 - \usepackage{fancyhdr} # modify header into left, center, right
 - \pagestyle{fancy} # cues the use of fancy headers
 - \fancyfoot{} # cues the use of fancy footer
 - \fancyhead[L]{EEC MS Thesis Draft} # month & year on header left 
 - \fancyhead[R]{p. \thepage} # name and page on header right
 - \usepackage{subcaption}
 - \usepackage{float}
# # - \fancyfoot[R]{ }
# - \usepackage{setspace}{singlespace} # manipulate line spacing 
# - \usepackage{parskip} # manipulate indents and spacing before/after paragra phs 
# - \usepackage{xcolor} # changes colors of text
# # http://latexcolor.com/ to choose colors
# # define the colors used above with rgb codes
# - \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
# - \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
# # to center to top level (#) headings (my name) and change color of font
# # more info # https://www.ctan.org/pkg/sectsty
# - \usepackage{sectsty}
# - \sectionfont{\centering\color{darkmidnightblue}}
# # to center to sub-sub-headings (###) and change color of font
# - \usepackage{sectsty} 
# - \subsectionfont{\centering\color{darkmidnightblue}}
# - \usepackage{sectsty} 
# - \subsubsectionfont{\raggedright\color{darkmidnightblue}}
# - \usepackage{wrapfig} 
# - \newcommand{\blandscape}{\begin{landscape}}
# - \newcommand{\elandscape}{\end{landscape}}
# - \usepackage[font=small,labelfont=bf]{caption} #Required for specifying captions to tables and figures
# - \usepackage{indentfirst}
# - \setlength\parindent{22pt} # uncomment if you want indented paragraphs
bibliography: ["eric-thesis.bib"]
output:
  pdf_document:
    includes:
      # in_header: style/preamble.tex
      template: null
      keep_tex: no
      extra_dependencies: ["float"]
      # number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(here)
library(tidyverse)
library(kableExtra)
library(grateful)
library(knitr)
# library(grid)
# library(gridExtra)
# library(png)
# library(egg)
# library(magick)
# library(citr)
# library(devtools)
# devtools::install_github("crsh/papaja")
cite_packages(citation.style = "peerj", out.dir = ".")
```

@@

# Abstract

@@

Next assignment:

~~1) Are any of the Dung Beetles we collected considered "open habitat" specialists? (might want to look at the work on pastures in the southeast)~~

- cvig - open sand chaparral, open grassland preference nealis 1977
- mbis - open sand chapparal preference nealis 1977
- open - slight preference towards open chap and shaded chap, little open grassland nealis 1977

- pign - sharing forest habitat but need more info conover 2019
- pvin - open habitat but share forest with pign conover 2019
- alec - forest preference conover 2019

~~2) Is there anything about these species that might be interesting in the context of corridors? Are any species known to be good fliers/movers? Specialists on deer dung? navigate by starlight?~~

  - Ospina 2018: wing shape py habitat preference and differences in wing shape determined by species groupings. Beetles with wider wings showed more preference towards open habitat, contrary to what is already known in literature on other taxa (butterflies). Large body beetles tending towards lower energy flight strategies. maybe justification for corridor preference?
    - stanbrook and king 2022: tunnelers preferring open habitat and tunnelers also contributing more towards dung removal. 
    - Conover 2019: dung source being less of an issue than habitat type but some species were more responsive to specific bait types so future studies should use a mix of multiple bait types 
    - Gimenez Gomez et al 2021 -> similar outcome some beetles were extra sensitive to specififc baits so a mix of baits should be used. However this study was done in a more tropical ecosystem so its hard to say if the same would apply to our more temperate system so more work is needed in this specific avenue.

3) Did you get any species not captured in other long-leaf/SE USA forest sites?

~~4) What are hill numbers?~~

- hill numbers are a set of biodiversity metrics designed to standardize metrics and quantify biodiversity and richness differently depending on how we want to emphasize abundance while also accounting for differences in sampling sizes and efforts (read more about this Eric)

~~5) What is the advantage of useing hill numbers to estimate diversity / richness?~~

- Chao et al. 2014: incorporating abundance into calculating diversity metrics is important for studying functionality in particular since some species that may not be as abundant as others may not contribute to an ecosystem function as much as others. At the same time rare species may be filling a specific niche or we might be concerned about exotics or at risk species.

6) Are the diversity and richness estimates calculated with hill numbers sensitive to anything, e.g., rare species/abundance, etc:

7) Find me the best example paragraph you think you read describing the use of hill numbers to estimate diversity/richness (field survey paper): _________________

8) Find me the best TWO description of using GLMM to compare abundance/diversity/richness at the Corridor Project: _________________

### Methods:

1. ~~add a few sentences on drying, keys used to ID, and depositing vouchers~~

1. ~~Write a short paragraph on how you calculated and compared species richness and diversity (hill numbers, glmm).~~

1. Write a short paragraph on how you calculated and compared functional diversity (how you measured it, how you compared it)

### Results

1. answer the overview questions, them stich them together into a paragraph

 - ~~any species restricted to 1-2 habitat types~~
 - ~~Were all species found in all blocks? Were any restricted to only 1-2 blocks?~~
 - ~~Were all species found in the matrix? (expect that so, since it is the 'baseline' or 'source' habitat)~~
 - Number of species in each functional group
 - ~~most common 3-4 species~~
 - any rare species? 
 - any invasive / exotic species?

### Figures

1. ~~Figure of species richness results.~~
1. Figure of species diversity results.
1. Figure of biomass of different (R/T/D) functional groups.
1. ~~Figure of abundance of individual species.~~
1. ~~Figure of the patch layout with pitfalls.~~

### Tables

1. ~~Table: count by species by habitat.~~
1. table: results of species richness analyses.
1. table: results of species diversity analyses.
1. table: results of functional diversity analyses.

### Misc.

1. Map of where field site is located.

1. Pictures of different species, sampling, field sites

@@

# INTRODUCTION

@@

**Paragraph 5:** Here is what we did to address this unknown. _The hypotheses we tested_

# Methods

## Study site

@@

## Dung beetle sampling

@@

## Analyses

@@

# RESULTS

@@

## Overview: Community Composition and Abundance

@@

# DISCUSSION

## Recap main goals into findings

@@

## Abundance

@@

We also observed that patch effects were not equally proportional for all species. The abundances of all dominant species were positively influenced by matrix habitat, but _Aphoidius alloblackburneus_ responded more positively than any other species. _Phanaeus igneus_ and _Ateuchus lecontei_ also had higher positive effects in rectangle patches. .

## Richness

@@

##Diversity

@@

 - habitat preference and seasonality (conover 2019, nealis 1977)
 - habitat again but  only part of variation form habitat specifically aphodius also phenology(roslin 2001)
 - spatial scales (roslin 2000)
 - morphology (ospina 2018)
 - functionality especially gas emissions (slade 2016)
 - species id and funcitonality (slade 2017)
 - faovored species dominating in fragments (resasco 2014)
 - wind direction in corridors (damschen 2014)

@@

## Interpretation of results

@@

# ACKNOWLEDGMENTS

@@

# REFERENCES

@@

\newpage
# FIGURES & TABLES

1. ~~Table: count by species by habitat.~~
1. ~~table: results of species richness analyses.~~
1. ~~Figure of species richness results.~~
1. ~~table: results of species diversity analyses.~~
1. ~~Figure of species diversity results.~~
1. table: results of functional diversity analyses.
1. Figure of biomass of different (R/T/D) functional groups.
1. ~~Map of where field site is located~~
1. ~~Figure of the patch layout with pitfalls~~.
1. ~~Pictures of different species, sampling, field sites?~~

@@

bray<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/bray_patches.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Bray-Curtis dissimilarity comparing composition of dung beetles between patches.") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
bray
```

@@

```{r Table aovMO, echo=FALSE,message = FALSE,warning=FALSE}

aovM0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM0
```

```{r Table MO, echo=FALSE,message = FALSE,warning=FALSE}

M0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M0
```

```{r Table aovMO3, echo=FALSE,message = FALSE,warning=FALSE}

aovM3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM3
```

```{r Table M3, echo=FALSE,message = FALSE,warning=FALSE}

M3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M3
```

```{r Table M_rich, echo=FALSE,message = FALSE,warning=FALSE}

M_rich<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_rich.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Richness Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_rich
```

```{r Table M_shan, echo=FALSE,message = FALSE,warning=FALSE}

M_shan<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_shan.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Shannon Diversity Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_shan
```

```{r Table M_simp, echo=FALSE,message = FALSE,warning=FALSE}

M_simp<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_simp.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Simpson's Index Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_simp
```

@@

# OTHER REQUIRED TEXT

## Dedication 
To my family who never stopped supporting me along this journey, my friends who kept me company along the way, and my mentors at VCU who believed in me before I did myself.

## List of Abbreviations

1. SRS:	Savannah River Site. 
1. Another word:	And the list continues with another definition.

## Biographical Sketch

@@

Dung beetles have emerged as a model system with which to test spatial ecology hypotheses [@ros_how_2012; @roslin_dung_2000].They are an incredibly well studied group of insects which are well known for driving a multitude of ecosystem functions (Hasan et al. 2024). The removal, breakdown, and burial of animal feces drive important ecostystem interactions provided by dung beetles enhancing nutrient cycling and soil quality, the reduction of breeding sites for parasites, and a reduction in methane emissions from dung [@slade_disentangling_2016; @WOS:000350444300013]. Local assemblages of dung beetles can be species-rich with species comprising a broad range of functional traits (e.g., size, foraging style, resource-use) [@WOS:000891747700001]. Previous studies have shown that isolated patches of habitat frequently have lower dung beetle diversity and abundance than areas of continuous habitat, as well as documented their presence in linear strips of habitat that resemble corridors [@WOS:000707546700001].  Past studies have also focused on how landscape structure alters the community compositions of dung beetles[@WOS:000398662200001], yet large landscape scale experimental studies with carefully controlled and replicated treatments are non-existent for this model species.

>>>>

# date: "\\vspace{-1em}"
header-includes:
 # - \AtBeginDocument{\let\maketitle\relax} # this removes default title section
 - \usepackage{lineno}
 - \linenumbers
 - \usepackage[default]{sourcesanspro}
 - \usepackage{fancyhdr} # modify header into left, center, right
 - \pagestyle{fancy} # cues the use of fancy headers
 - \fancyfoot{} # cues the use of fancy footer
 - \fancyhead[L]{EEC MS Thesis Draft} # month & year on header left 
 - \fancyhead[R]{p. \thepage} # name and page on header right
 - \usepackage{subcaption}
 - \usepackage{float}
# # - \fancyfoot[R]{ }
 - \usepackage{setspace}
 # - doublespacing # manipulate line spacing 
# - \usepackage{parskip} # manipulate indents and spacing before/after paragra phs 
# - \usepackage{xcolor} # changes colors of text
# # http://latexcolor.com/ to choose colors
# # define the colors used above with rgb codes
# - \definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
# - \definecolor{darkmidnightblue}{rgb}{0.0, 0.2, 0.4}
# # to center to top level (#) headings (my name) and change color of font
# # more info # https://www.ctan.org/pkg/sectsty
# - \usepackage{sectsty}
# - \sectionfont{\centering\color{darkmidnightblue}}
# # to center to sub-sub-headings (###) and change color of font
# - \usepackage{sectsty} 
# - \subsectionfont{\centering\color{darkmidnightblue}}
# - \usepackage{sectsty} 
# - \subsubsectionfont{\raggedright\color{darkmidnightblue}}
# - \usepackage{wrapfig} 
# - \newcommand{\blandscape}{\begin{landscape}}
# - \newcommand{\elandscape}{\end{landscape}}
# - \usepackage[font=small,labelfont=bf]{caption} #Required for specifying captions to tables and figures
# - \usepackage{indentfirst}
# - \setlength\parindent{22pt} # uncomment if you want indented paragraphs
bibliography: ["eric-thesis.bib"]
output:
  pdf_document:
    includes:
      # in_header: style/preamble.tex
      template: null
      keep_tex: no
      extra_dependencies: ["float"]
      # number_sections: true
# documentclass: style/nsf2
biblio-style: apalike
csl: ecology.csl
---

@@

knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(here)
library(tidyverse)
library(kableExtra)
# library(grateful)
library(knitr)
# library(grid)
# library(gridExtra)
# library(png)
# library(egg)
# library(magick)
# library(citr)
# library(devtools)
# devtools::install_github("crsh/papaja")
# cite_packages(citation.style = "peerj", out.dir = ".")
```

@@

1) **Results:** Did you get any species not captured in other long-leaf/SE USA forest sites?

2) **Methods:** Find me the best example paragraph you think you read describing the use of hill numbers to estimate diversity/richness (field survey paper)

3) **Methods:** Find me the best TWO descriptions of using GLMM to compare abundance/diversity/richness at the Corridor Project

4) **Methods:** Write a short paragraph on how you calculated and compared functional diversity (how you measured it, how you compared it)

5) **Figure: ** biomass of different (R/T/D) functional groups.

6) **Table:** Results of functional diversity analyses.

YOUR TITLE GOES HERE 
IN UPPER CASE SINGLE SPACE

By

YOUR NAME GOES HERE IN ALL CAPITAL LETTERS

A THESIS PRESENTED TO THE GRADUATE SCHOOL OF THE UNIVERSITY OF FLORIDA IN PARTIAL FULFILLMENT OF THE REQUIREMENTS FOR THE DEGREE OF MASTER OF SCIENCE

UNIVERSITY OF FLORIDA

2025
\newpage

© 2025 Your Name Goes Here in Title Case

_Your dedication is typed here. It should begin with the word “To.”
(To my Mom is a typical dedication) If your dedication is longer than a single line it should be single-spaced, and centered vertically and horizontally_

To my family who never stopped supporting me along this journey, my friends who kept me company along the way, and my mentors at VCU who believed in me before I did myself.

ACKNOWLEDGMENTS
_Acknowledgments must be written in complete sentences. Do not use direct address. For example, instead of Thanks, Mom and Dad!, you should say I thank my parents._

LIST OF ABBREVIATIONS

A word to be defined: Write the definition here.

Another word:	Another def.

Another word:	Another def.

SRS:	Savannah River Site.

Abstract of Thesis Presented to the Graduate School  
of the University of Florida in Partial Fulfillment of the  
Requirements for the Degree of Master of Science.

TITLE OF THE WORK, CENTERED, SINGLE-SPACED,
IN ALL CAPITAL LETTERS, EXACTLY AS ON TITLE PAGE

By

Your Name as on the Title Page, but in Title Case.

Month and year of graduation

Chair: Name (Do not put Dr. before the name, and do not put degrees after it)  
Cochair: Name (if any, otherwise delete this line)  
Major: See your Editorial Document Management record for your exact major

@@

@@

\doublespacing

## CHAPTER 1

## TITLE OF CHAPTER ONE

## INTRODUCTION

@@

## Methods

### Study site

@@

### Dung beetle sampling

@@

@@

## RESULTS

@@

### Overview: Community Composition and Abundance

@@

## DISCUSSION

_Don't repeat results...tell us:

1) what your OVERALL conclusions are, 
2) HOW your results compare to those of other studies, 
3) WHY they are similar and / or different
4) BIOLOGICAL INSIGHTS you might have gained about partiicular species
5) any CAVEATS to your results or shortcomings of your study
6) the NEXT STEPS you recommend be taken by researchers interested in this toopic or system

@@

### Abundance

@@

We also observed that patch effects were not equally proportional for all species. The abundances of all dominant species were positively influenced by matrix habitat, but _Aphoidius alloblackburneus_ responded more positively than any other species. _Phanaeus igneus_ and _Ateuchus lecontei_ also had higher positive effects in rectangle patches.

### Richness

@@

### Diversity

@@

 - habitat preference and seasonality (conover 2019, nealis 1977)

> - cvig - open sand chaparral, open grassland preference nealis 1977
> - mbis - open sand chapparal preference nealis 1977
> - open - slight preference towards open chap and shaded chap, little open grassland nealis 1977

> - pign - sharing forest habitat but need more info conover 2019
> - pvin - open habitat but share forest with pign conover 2019
> - alec - forest preference conover 2019

 - habitat again but  only part of variation form habitat specifically aphodius also phenology (roslin 2001)
 - spatial scales (roslin 2000)
 - morphology

> - Ospina 2018: wing shape py habitat preference and differences in wing shape determined by species groupings. Beetles with wider wings showed more preference towards open habitat, contrary to what is already known in literature on other taxa (butterflies). Large body beetles tending towards lower energy flight strategies. maybe justification for corridor preference?
> - stanbrook and king 2022: tunnelers preferring open habitat and tunnelers also contributing more towards dung removal. 
> - Conover 2019: dung source being less of an issue than habitat type but some species were more responsive to specific bait types so future studies should use a mix of multiple bait types 
> - Gimenez Gomez et al 2021 -> similar outcome some beetles were extra sensitive to specififc baits so a mix of baits should be used. However this study was done in a more tropical ecosystem so its hard to say if the same would apply to our more temperate system so more work is needed in this specific avenue.

 - functionality especially gas emissions (slade 2016)
 - species id and funcitonality (slade 2017)
 - faovored species dominating in fragments (resasco 2014)
 - wind direction in corridors (damschen 2014)

@@

---

Discussion Outline & Notes

@@

@@

## REFERENCES

@@

\newpage
## FIGURES & TABLES

@@

# bray<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/bray_patches.csv") 
bray<-read_csv(here("corridor_docs","eric_ms_thesis","tables","bray_patches.csv")) %>% kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Bray-Curtis dissimilarity comparing composition of dung beetles between patches.") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
bray
```

@@

```{r Table aovMO, echo=FALSE,message = FALSE,warning=FALSE}
aovM0<-read_csv(here("corridor_docs","eric_ms_thesis","tables","aovM0.csv")) %>%
# aovM0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM0
```

```{r Table MO, echo=FALSE,message = FALSE,warning=FALSE}
M0<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M0.csv")) %>%
# M0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M0
```

```{r Table aovMO3, echo=FALSE,message = FALSE,warning=FALSE}
aovM3<-read_csv(here("corridor_docs","eric_ms_thesis","tables","aovM3.csv")) %>%
# aovM3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM3
```

```{r Table M3, echo=FALSE,message = FALSE,warning=FALSE}
M3<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M3.csv")) %>%
# M3<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M3.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M3
```

```{r Table M_rich, echo=FALSE,message = FALSE,warning=FALSE}
M_rich<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_rich.csv")) %>%
# M_rich<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_rich.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Richness Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_rich
```

```{r Table M_shan, echo=FALSE,message = FALSE,warning=FALSE}
M_shan<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_shan.csv")) %>%
# M_shan<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_shan.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Shannon Diversity Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_shan
```

```{r Table M_simp, echo=FALSE,message = FALSE,warning=FALSE}
M_simp<-read_csv(here("corridor_docs","eric_ms_thesis","tables","M_simp.csv")) %>%
# M_simp<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/M_simp.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Simpson's Index Model") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
M_simp
```

@@

# BIOGRAPHICAL SKETCH

_A biographical sketch is required of all candidates. The biographical sketch should be in narrative form. Third person, past tense, it typically includes the educational background of the candidate. The author should have replaced this paragraph with their own._

@@

Dung beetles have emerged as a model system with which to test spatial ecology hypotheses [@ros_how_2012; @roslin_dung_2000].They are an incredibly well studied group of insects which are well known for driving a multitude of ecosystem functions (Hasan et al. 2024). The removal, breakdown, and burial of animal feces drive important ecostystem interactions provided by dung beetles enhancing nutrient cycling and soil quality, the reduction of breeding sites for parasites, and a reduction in methane emissions from dung [@slade_disentangling_2016; @WOS:000350444300013]. Local assemblages of dung beetles can be species-rich with species comprising a broad range of functional traits (e.g., size, foraging style, resource-use) **(citation)**. Previous studies have shown that isolated patches of habitat frequently have lower dung beetle diversity and abundance than areas of continuous habitat, as well as documented their presence in linear strips of habitat that resemble corridors [@WOS:000707546700001].  Past studies have also focused on how landscape structure alters the community compositions of dung beetles[@WOS:000398662200001], yet large landscape scale experimental studies with carefully controlled and replicated treatments are non-existent for this model species.
